### 2017-03-30 Writing/device.tex
Update

Although network protocols are generally implemented independently to hardware, there are still ways the information could leak through the traffic meta data. For instance, when the default MAC address of a device is used, one can be immediately look up the manufacturer by the Burned-In Address (BIA)\cite{BIA}.

Different driver implementations may also leak. Among the platforms we tested, we realised that TelosB\cite{TelosB} discards all packets exceeding 127 bytes\footnote{MTU specified by 802.15.4 standard.}; whereas CC2538 is capable of handling packets even up to 160 bytes. Therefore an adversary can immediately rule out TelosB when any packet larger than 127 bytes is observed.

%Now it comes to PING.
A more general leakage is the response latency to a specific message, as different processors would have different computational power and thus different time to process the message. The ICMP messages turns out to vulnerable targets against this attack for they are standardised and widely supported. PING is especially ideal for two reasons: 
\begin{enumerate}
	\item It is mandatory in the ICMP standard.
	\item It only swaps the source and destination address of the packet; thus minimises different code path in protocol processing.
\end{enumerate}

>>>>

Although network protocols are generally implemented independently to hardware, information could still leak through various ways. For instance, when the default MAC address is used, one can immediately look up the manufacturer by the Burned-In Address (BIA)\cite{BIA}.

Different driver implementations may also cause leakage. During the experiments, we realised that TelosB\cite{TelosB} discards all packets exceeding 127 bytes\footnote{MTU specified by 802.15.4 standard.}; whereas CC2538 is capable of handling packets even up to 160 bytes. Therefore an adversary can immediately rule out TelosB when any packet larger than 127 bytes is observed.

%Now it comes to PING.
A more general leakage is the response latency to a specific message, as different processors would have different computational power and thus different time to process a same message. The ICMP messages turns out to be suitable for this attack since they are standardised and thus universally supported. Among the ICMP messages, PING is especially ideal for two reasons: 
\begin{enumerate}
	\item It is mandatory in the ICMP standard.
	\item It only swaps the source and destination address of the packet; thus minimises different code path in protocol processing.
\end{enumerate}
